### 2010-03-25 papers/icfp-2010-desc/paper_discussion.tex
Desc@ICFP: related work: bring references in paper.bib

\begin{wstructure}
!!! Need Help !!!
<- Related Work
    Who? What?
\end{wstructure}

>>>>

\begin{wstructure}
!!! Need Help !!!
<- Related Work
    <- Generic in simply-typed functional languages
        <- PolyP \cite{jansson:polyp}
        <- Generic Haskell \cite{hinze:generic-haskell}
        <- Scratch your boilerplate \cite{spj:syb}
    <- Generic in dependent types
        <- Universes for generic prog \cite{benke:universe-generic-prog}
        <- Norell \cite{norell:msc-thesis}
        <- Polytypic prog in Coq \cite{verbruggen:polytype-coq}
\end{wstructure}
